
---
title: "Base R- Weekly Assignment #1"
author: "Connor Prok"
date: "2022-09-29"
output: html_document
---

1. Name the four panels in R Studio and offer a brief description of each.

Main panel - where all your code and information is located. Shows you what you are working on. 
Bottom left -The console which runs a lot of the "behind the scenes" information. Install packages and run code that doesn't affect the main terminal. "Scratch paper".
Top right - Has everything and is an overview of the console. Contains data, datasets, vectors, variables, etc. Tutorials and history as well
Bottom right - Basically has everything else including tons of information on different packages and how different functions in R work and function. 
#√
2. Create a code chunk. Write your favorite number in it. 

```{r}
8
```
#√

3. Add thirty-seven to six

```{r}
6+37
```

#√
4. evaluate the following: six times four is equal to twenty-four

```{r}
6*4 == 24
#True
```
#√

5. What's the difference between an "and" and an "or" statement? 

An "and" statement will be based on true/false based on both conditional statements while an "or" statement depends on only one being true to be labeled as true. For example, a building is a structure and a car is a delectable will come back with a false message because of the second statement. Meanwhile if you run this with an "or" statement, it would come back true (theoretically, with some manipulations to the variables)
#√
6. Create an "and" statement for the following sentence: three is less than five and tree is the same as oak. 

```{r}
3 < 5 & "tree" == "oak"
#False
```
#√

7. Create a variable called "dinner" that contains your favorite thing to eat for dinner. 

```{r}
dinner <- "steak"
dinner
```
#√

8. write out all numbers between 50 and 200

```{r}
50:200
```
#√

9. print every odd number between 1 and 300. 

```{r}
seq(1, 300, 2)
```
#√

10. repeat the phrase "i'm excited for fall" five times

```{r}
rep("I'm excited for fall", 5)
```

#√
